Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2023-05-11 Manuscript/Manuscript.Rmd
Add key_resource_table

@@

@@

>>>>

##Key resources table

```         
library(readxl)
NOSpaper_keyresourcetale <- read_excel("source_data/key_resource_tale.xlsx")

{r echo=FALSE,fig.cap="**Key resources table** "}
```

@@

```{r echo=FALSE,fig.cap="**Figure 1 -- figure supplement 3** "}
knitr::include_graphics(path = "figures/Fig1_sup3.png")

@@

```{r echo=FALSE,fig.cap="**Figure 4 -- figure supplement 3** "}
knitr::include_graphics(path = "figures/Fig4_sup3.png")
